Global adjoint tomography -- Model GLAD-M25

### 2018-10-22 main.tex
Updates from ShareLaTeX

Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, togthere with 3 global models,
S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted}, while the latter two are
global $V_p$ models.

At 100km depth, the northern part of South America is covered by large area
of lithosphere craton, showing fast wave anomaly except GAP-P4. The fast anomaly
stays strong in LLNL-G3Dv3 while for GLAD-M25
and S362ANI+M it disappear at such depth.
At 300km, we are see a sharpened fast anomaly in the south subduction area
in GLAD-M25 compared to S372ANI+M. However, the shape and strength are very close
between GLAD-M25 and LLNL-G3Dv3 models. Moving to even larger depth, the features of
subcutions becomes divergent between the north Peruvian slab and south Chilean slab.
At 600km, we observed a large chunck of fast anomaly in the Chilean slab,
indicating the slab is trapped and stagnant in the mantle transition zone. However,
the Peruvian slabs has penertrated the mantle transition zone and extend till 1000,
reaching the uppermost part of lower mantle, which is consistent with GAP-P4
\citep{fukao2013subducted}.

Besides, in the Pacific and Nazca plate, our models is sharpening the Galapagos,
San Felix and Juan Fernandez hotspot. In the Scotia plate, our models shows a very
strong expression of Scotia Arc subduciton till 1000km, which is barely observable
in other models. In the Carribean plate, we also observed fast anomaly, indicating
the carribean subduction.

>>>>

Fig.\ref{fig:southamerica-vp} shows the $V_p$ velocity in our model, together with 3
global models, S362ANI+M, LLNL-G3Dv3\citep{}, GAP-P4\citep{fukao2013subducted},
while the latter two are global $V_p$ models.

At 100km depth, the northern part of South America is covered by large area
of lithosphere craton, showing fast wave anomaly except GAP-P4. The fast anomaly
stays strong in LLNL-G3Dv3 while for GLAD-M25
and S362ANI+M it disappear at such depth.
At 300km, we are see a sharpened fast anomaly in the south subduction area
in GLAD-M25 compared to S372ANI+M. However, the shape and strength are very close
between GLAD-M25 and LLNL-G3Dv3 models. Moving to even larger depth, the features of
subductions becomes divergent between the north Peruvian slab and south Chilean slab.
At 600km, we observed a large chunk of fast anomaly in the Chilean slab,
indicating the slab is trapped and stagnant in the mantle transition zone. However,
the Peruvian slabs has penetrated the mantle transition zone and extend till 1000,
reaching the uppermost part of lower mantle, which is consistent with GAP-P4
\citep{fukao2013subducted}.

Besides, in the Pacific and Nazca plate, our models is sharpening the Galapagos,
San Felix and Juan Fernandez hotspot. In the Scotia plate, our models shows a very
strong expression of Scotia Arc subduction till 1000km, which is barely observable
in other models. In the Caribbean plate, we also observed fast anomaly, indicating
the Caribbean subduction.
